Computer Science House Constitution

### 2025-09-10 constitution.tex

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.

>>>>

\asubsection{Eligible Votes}
The number of Active Members who are eligible to vote on the issue.
Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
